Improving the Accuracy of a Sequential Mining Model for Hurricane Trajectory Prediction

### 2018-02-15 paper/manuscript_revised.tex
Modify drawing script to render figures with proper dimensions. Save those figures.

% Figures 2 and 3: Trajectories without and with region overlay
\begin{figure}[htp]
\caption{Hurricane Trajectory Paths Without and With Regionalization}
\centering
\includegraphics[scale=0.55]{Merged-Trajectory-Comparison}
\end{figure}

Consider figure (2), generated using a sample of the recorded hurricane trajectories in HURDAT2 with the visualization tool Matplotlib \cite{matplotlib}. As shown in the pair of images, region discretization organizes continuous hurricane coordinate sequences into discrete region sequences of approximately uniform size and square shape. A discretization block size of 5 is selected in HTPDM and is replicated in WARD-HTP. A block size of 5 corresponds approximately to a real-world block dimension of 500km by 500km. The block dimension size is approximate because the mapping between coordinate degrees and kilometres is imprecise, and is dependent on location in the case of longitudinal points \cite{lat-long-distance}. The approximate size of 500km is similar to the average hurricane total diameter \cite{hurricane-distances}, permitting the coarse-grain expression of hurricane trajectories without undue loss in precision.

@@

\begin{figure}[htp]
\caption{Non-Matchable Hurricane Trajectory Paths}
\centering
\includegraphics[scale=0.6]{Rule-Miss-Diagram}
\end{figure}

Figure (3) illustrates the characteristics of trajectories which were not able to match with any interesting rules. The particular diagram was generated from training data ranging from 1950 to 2000, and testing data from 2001 to 2015. Red trajectories represent a subset of the training data, while blue trajectories are those which did not match with any association rules. It is visually clear to see that non-matching trajectories were highly dissimilar from training data trajectories. As a result, no amount of point extrapolation would be able to result in a reliable terminal trajectory prediction. Some of the non-matching trajectories appear to align with training trajectories, but are moving in an opposite direction. Therefore, any points that matched such trajectories would also not provide a reliable result.

>>>>

% Figures 2 and 3: Trajectories without and with region overlay
% \begin{figure}[htp]
% \caption{Hurricane Trajectory Paths Without and With Regionalization}
% \centering
% \includegraphics[scale=0.55]{Merged-Trajectory-Comparison}
% \end{figure}

\begin{figure}[htp]
\caption{Hurricane Trajectory Paths Without and With Regionalization}
\centering
\includegraphics[scale=0.55]{Trajectories-Proper-Range-Regions-NoRegions-Combined}
\end{figure}

Consider figure (2), generated using a sample of the recorded hurricane trajectories in HURDAT2 with the visualization tool Matplotlib \cite{matplotlib}. The region of interest is captured within the emboldened sections of the figures. As shown in the pair of images, region discretization organizes continuous hurricane coordinate sequences into discrete region sequences of approximately uniform size and square shape. A discretization block size of 5 is selected in HTPDM and is replicated in WARD-HTP. A block size of 5 corresponds approximately to a real-world block dimension of 500km by 500km. The block dimension size is approximate because the mapping between coordinate degrees and kilometres is imprecise, and is dependent on location in the case of longitudinal points \cite{lat-long-distance}. The approximate size of 500km is similar to the average hurricane total diameter \cite{hurricane-distances}, permitting the coarse-grain expression of hurricane trajectories without undue loss in precision.

@@

\begin{figure}[htp]
\caption{Non-Matchable Hurricane Trajectory Paths}
\centering
\includegraphics[scale=0.6]{Trajectories-Proper-Range-Show-Miss}
\end{figure}

Figure (3) illustrates the characteristics of trajectories which were not able to match with any interesting rules. As seen in figure (2), the area of interest to this work is captured within the bold area. The particular diagram was generated from training data ranging from 1950 to 2000, and testing data from 2001 to 2015. Red trajectories represent a subset of the training data, while blue trajectories are those which did not match with any association rules. It is visually clear to see that non-matching trajectories were highly dissimilar from training data trajectories. As a result, no amount of point extrapolation would be able to provide a reliable terminal trajectory prediction. Some of the non-matching trajectories appear to align with training trajectories, but are moving in an opposite direction. Therefore, any points that matched such trajectories would also not provide a reliable result.
